Software Citation Principles

### 2016-06-23 sc-principles/software-citation-principles.tex
remove "permit and" to close issue #138

\item \textbf{Accessibility}: \label{principle:accessibility} Software citations
should permit and facilitate access to the software itself and to its
associated metadata, documentation, data, and other materials necessary
for both humans and machines to make informed use of the referenced software.

>>>>

\item \textbf{Accessibility}: \label{principle:accessibility} Software citations
should facilitate access to the software itself and to its
associated metadata, documentation, data, and other materials necessary
for both humans and machines to make informed use of the referenced software.
